---
title: "MP#4"
author: "Vanessa, Kareen, and Maggie"
date: "May 10, 2018"
output:
  html_document:
    code_folding: hide
---
#Loading the libraries

```{r warning=FALSE, message=FALSE}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```
```{r}
library(ggplot2)
```

```{r}
class(db)
```

#Query from SQL to get a table with the title of movies, production year, and genre. the title table is joined to the movie_info table. the info_type_id = 3 to get information about the genre in the movie_info table
```{r}
db %>%
  dbGetQuery("SELECT  title,production_year,info  
FROM title
JOIN movie_info ON movie_id = title.id
WHERE info_type_id = 3;")
```

#Looking for trends in comedy genre over four decades
```{r}
db <- dbConnect_scidb(dbname = "imdb")
Data_Comedy <- db %>%
  dbGetQuery ("SELECT (10 * floor (production_year/ 10)) AS Decades, count(*) AS Count, info AS Genre
FROM title
JOIN movie_info ON movie_id = title.id
WHERE info_type_id = 3
AND info LIKE '%comedy%'
AND kind_id = 1
AND  production_year >= 1980
      AND production_year <=  2015
GROUP BY Decades;")
```
```{r}
graph <- ggplot(Data_Comedy,aes(x = Decades, y = Count)) + 
  geom_line() +
labs(title = "Comedy Films", x ="Production_by_Decades", y = "Count")
graph + theme(panel.background = element_rect(fill = "white", colour = "red", size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5,
                                  linetype = "solid",
                                  colour = "white"),
  panel.grid.minor = element_line(size = 0.25,
                                  linetype = 'solid',
                                  colour = "white"))
```


#Looking for trends in musical genre over four decades
```{r}
db <- dbConnect_scidb(dbname = "imdb")
Data_musical<- db %>%
  dbGetQuery ("SELECT (10 * floor (production_year/ 10)) AS Decades, count(*) AS Count, info AS Genre
FROM title
JOIN movie_info ON movie_id = title.id
WHERE info_type_id = 3
AND info LIKE '%musical%'
AND kind_id = 1
AND  production_year >= 1980
      AND production_year <=  2015
GROUP BY Decades;")
```
```{r}
graph <- ggplot(Data_musical,aes(x = Decades, y = Count)) + 
  geom_line() +
labs(title = "Musical", x ="Production_by_Decades", y = "Count")
graph + theme(panel.background = element_rect(fill = "white", colour = "red", size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5,
                                  linetype = "solid",
                                  colour = "white"),
  panel.grid.minor = element_line(size = 0.25,
                                  linetype = 'solid',
                                  colour = "white"))
```

#Looking for trends in sci-fi genre over four decades
```{r}
db <- dbConnect_scidb(dbname = "imdb")
Data_scifi<- db %>%
  dbGetQuery ("SELECT (10 * floor (production_year/ 10)) AS Decades, count(*) AS Count, info AS Genre
FROM title
JOIN movie_info ON movie_id = title.id
WHERE info_type_id = 3
AND info LIKE '%sci-fi%'
AND kind_id = 1
AND  production_year >= 1980
      AND production_year <=  2015
GROUP BY Decades;")
```
```{r}
graph <- ggplot(Data_scifi,aes(x = Decades, y = Count)) + 
  geom_line() +
labs(title = "Sci-fi", x ="Production_by_Decades", y = "Count")
graph + theme(panel.background = element_rect(fill = "white", colour = "red", size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5,
                                  linetype = "solid",
                                  colour = "white"),
  panel.grid.minor = element_line(size = 0.25,
                                  linetype = 'solid',
                                  colour = "white"))
```

#Looking for trends in action films over four decades
```{r}
db <- dbConnect_scidb(dbname = "imdb")
Data_action <- db %>%
  dbGetQuery ("SELECT (10 * floor (production_year/ 10)) AS Decades, count(*) AS Count, info AS Genre
FROM title
JOIN movie_info ON movie_id = title.id
WHERE info_type_id = 3
AND info LIKE '%action%'
AND kind_id = 1
AND  production_year >= 1980
      AND production_year <=  2015
GROUP BY Decades;")
```

```{r}
graph <- ggplot(Data_action,aes(x = Decades, y = Count)) + 
  geom_line() +
labs(title = "Action Films", x ="Production_by_Decades", y = "Count")
graph + theme(panel.background = element_rect(fill = "white", colour = "red", size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5,
                                  linetype = "solid",
                                  colour = "white"),
  panel.grid.minor = element_line(size = 0.25,
                                  linetype = 'solid',
                                  colour = "white"))
```

#Putting all four genres in one graph for comparison 
```{r}
All_Films <- bind_rows(
  Data_action, Data_Comedy,
  Data_musical, Data_scifi)

ggplot(All_Films, aes(x = Decades, y = Count, color = Genre)) + 
         geom_line()

```





